Diversity dynamics in Nymphalidae butterflies: Effect of phylogenetic uncertainty on diversification rate shift estimates

### 2015-01-14 response_to_reviewers.tex

\textbf{32. Response:}
\begin{quote}
\color{blue}
We replaced the word according to the reviewer's suggestion:
\end{quote}

\textbf{33. Reviewer's Comment:}
Page 10, second full paragraph, third sentence: 2 changes; (A) replace “the
trait 'feeding on Solanaceae'” to “Solanaceae-feeding”; (B) add qualifier
“likely”: “was likely important in the diversification...”

\textbf{33. Response:}
\begin{quote}
\color{blue}
We revised the paragraph according to the reviewer's suggestions.
\end{quote}

\textbf{34. Reviewer's Comment:}
Page 10, second full paragraph, fifth sentence: replace “the trait 'feeding on
Apocynaceae'” with “Apocynaceae-feeding”.

\textbf{34. Response:}
\begin{quote}
\color{blue}
We revised the paragraph according to the reviewer's suggestion.
\end{quote}

\textbf{35. Reviewer's Comment:}
Page 10, Figure legends, figure 1: Include a description of what nodes 1 and
19 are as well.

\textbf{35. Response:}
\begin{quote}
\color{blue}
We added the description of nodes 1 and 19 to the legend as suggested by the
reviewer.
\end{quote}

### 2015-01-14 MS_revised.tex
comment 34
comment 35

Our MultiMEDUSA approach to perform analyses on the posterior
distribution of trees found strong support for an increase in net
diversification rate in the tribe Ithomiini, the genera \emph{Ypthima},
\emph{Charaxes}, the clade \emph{Callicore} + \emph{Diaethria} and for a
decrease in net diversification rate in the
subtribe Danaina. Due to phylogenetic uncertainty, we did not obtain
strong support for other diversification shifts in Nymphalidae. Our
BiSSE analysis corroborated other studies in that Solanaceae-feeding,
or a codistributed character, was likely important in the
diversification of Ithomiini butterflies. However, by applying MEDUSA we
found that a critical character in the radiation of the group might have
appeared after the shift from Apocynaceae to Solanaceae. We also found
that the trait ``feeding on Apocynaceae'' is not responsible for the
slowdown of diversification in Danaina. Ithomiini and Solanaceae
diversified near simultaneously, which is in agreement with the diffuse
cospeciation hypothesis \cite{nyman2012, janz2011}.

@@

\section*{Figure legends}
{\bf Figure 1. Results of the MEDUSA analysis run on the maximum
clade credibility tree from Wahlberg et al. (2009)} Rate shifts were estimated for the
following nodes (besides the background rate): 2) Limenitidinae +
Heliconiinae, 3) \emph{Ypthima}, 4) \emph{Charaxes}, 5) Ithomiini in
part, 6) Satyrinae, 7) Coenonymphina 8) Phyciodina in part, 9) Danaini in
part, 10) \emph{Coenonympha}, 11) \emph{Caeruleuptychia} +
\emph{Magneuptychia}, 12) \emph{Callicore} + \emph{Diaethria}, 13)
Satyrina, 14) Mycalesina, 15) \emph{Pedaliodes}, 16) \emph{Dryas} +
\emph{Dryadula}, 17) \emph{Taenaris}, 18) Pseudergolinae. Circles on
nodes indicate the diversification shift number as found by MEDUSA.
Numbers next to circles indicate the posterior probability values for
such nodes.

>>>>

Our MultiMEDUSA approach to perform analyses on the posterior
distribution of trees found strong support for an increase in net
diversification rate in the tribe Ithomiini, the genera \emph{Ypthima},
\emph{Charaxes}, the clade \emph{Callicore} + \emph{Diaethria} and for a
decrease in net diversification rate in the
subtribe Danaina. Due to phylogenetic uncertainty, we did not obtain
strong support for other diversification shifts in Nymphalidae. Our
BiSSE analysis corroborated other studies in that Solanaceae-feeding,
or a codistributed character, was likely important in the
diversification of Ithomiini butterflies. However, by applying MEDUSA we
found that a critical character in the radiation of the group might have
appeared after the shift from Apocynaceae to Solanaceae. We also found
that Apocynaceae-feeding is not responsible for the
slowdown of diversification in Danaina. Ithomiini and Solanaceae
diversified near simultaneously, which is in agreement with the diffuse
cospeciation hypothesis \cite{nyman2012, janz2011}.

@@

\section*{Figure legends}
{\bf Figure 1. Results of the MEDUSA analysis run on the maximum
clade credibility tree from Wahlberg et al. (2009)} Rate shifts were estimated for the
following nodes (besides the background rate): 1) root, 2) Limenitidinae +
Heliconiinae, 3) \emph{Ypthima}, 4) \emph{Charaxes}, 5) Ithomiini in
part, 6) Satyrinae, 7) Coenonymphina 8) Phyciodina in part, 9) Danaini in
part, 10) \emph{Coenonympha}, 11) \emph{Caeruleuptychia} +
\emph{Magneuptychia}, 12) \emph{Callicore} + \emph{Diaethria}, 13)
Satyrina, 14) Mycalesina, 15) \emph{Pedaliodes}, 16) \emph{Dryas} +
\emph{Dryadula}, 17) \emph{Taenaris}, 18) Pseudergolinae, 19)
\emph{Anaeomorpha} + \emph{Hypna}. Circles on
nodes indicate the diversification shift number as found by MEDUSA.
Numbers next to circles indicate the posterior probability values for
such nodes.
